Finite-state morphological transducers for three Kypchak languages

### 2014-03-22 kipchak-lrec-2013/kipchak-paper.tex
apertium-kaz/tat/kum in \texttt{}
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51108 72bbbca6-d526-0410-a7d9-f06f51895060

%FIXME: keep revision number up to date
The transducers are available / under development in apertium's subversion repository,\footnote{{\scriptsize \url{https://svn.code.sf.net/p/apertium/svn/languages/}}} in the directories apertium-kaz, apertium-tat, and apertium-kum, and compiled versions may be run at \url{http://turkic.apertium.org/}.  The revision of each module in the subversion repository that the numbers in this paper (stem counts, evaluation, etc.) represent is \texttt{r50547} for Kazakh, \texttt{r50260} for Tatar, and \texttt{r50300} for Kumyk.

@@

\begin{figure}
%\centering
%\hspace{-35pt}
%\hspace{-1em}
%    \rotatebox{-90}{
%\hspace{-15pt}
\hspace{-10pt}
\includegraphics[width=0.37\textwidth,bb=50 50 554 770,angle=270]{graphs/kumyk-yoldash-coverage}
%}
%~\\
%~\\

>>>>

%FIXME: keep revision number up to date
The transducers are available / under development in apertium's subversion repository,\footnote{{\scriptsize \url{https://svn.code.sf.net/p/apertium/svn/languages/}}} in the directories \texttt{apertium-kaz}, \texttt{apertium-tat}, and \texttt{apertium-kum}, and compiled versions may be run at \url{http://turkic.apertium.org/}.  The revision of each module in the subversion repository that the numbers in this paper (stem counts, evaluation, etc.) represent is \texttt{r50547} for Kazakh, \texttt{r50260} for Tatar, and \texttt{r50300} for Kumyk.

@@

\begin{figure}
%\centering
\hspace{-35pt}
%\hspace{-1em}
%    \rotatebox{-90}{
%\hspace{-15pt}
\hspace{-10pt}
\includegraphics[width=0.37\textwidth,bb=50 50 554 770,angle=270]{graphs/kumyk-yoldash-coverage}
%}
%~\\
%~\\
